PANCHANGE_data_preprocessing

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Tidied up script and chunk naming.

# glad gad (prepan)

```{r glad gad head}
if(GLAD ==TRUE | EDGI == TRUE){
head(prepan.gad.raw.id)
}
```

```{r glad gad summary}
if(GLAD ==TRUE | EDGI == TRUE){
summarytools::dfSummary(
  prepan.gad.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```

@@

# glad prepandemic pcl

@@

# edgi pcl

@@

```{r glad pcl head}
if(GLAD == TRUE | EDGI == TRUE){
head(prepan.pcl.raw.id)
}
```

```{r glad pcl summary}
if(GLAD == TRUE | EDGI == TRUE){
summarytools::dfSummary(
  prepan.pcl.raw.id,
  graph.col = F,
  valid.col = F, labels.col = F)
}
```

# glad phq

@@

# edgi phq

@@

```{r glad phq head}
if(GLAD == TRUE | EDGI == TRUE) {
head(prepan.phq.raw.id)
}
```

```{r glad phq summary}
if(GLAD == TRUE | EDGI == TRUE) {
summarytools::dfSummary(
  prepan.phq.raw.id,
  graph.col = F,
  valid.col = F
  )
}
```

# glad ocir

```{r glad ocir cols}
if(GLAD == TRUE){
glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_glad.rds"))
dim(glad.ocir.raw)
colnames(glad.ocir.raw)
}
```

```{r glad ocir cleaning}
if(GLAD == TRUE){
glad.ocir.raw.id <- glad.ocir.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
    ocir.arranged_things_prepan = ocir.arranged_things,
    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
    ocir.saved_things_prepan = ocir.saved_things,
    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

# edgi ocir

```{r edgi ocir cols}
if(EDGI == TRUE){
  edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_edgi.rds"))
  dim(edgi.ocir.raw)
  colnames(edgi.ocir.raw)
}
```

```{r edgi ocir cleaning}
if(EDGI == TRUE){
  edgi.ocir.raw.id <- edgi.ocir.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID),
           startDate.prepandemic = startDate) %>% # Rename startDate
    select(
      Sample, # Sample
      ID, # ID
      ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
      ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
      ocir.arranged_things_prepan = ocir.arranged_things,
      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
      ocir.saved_things_prepan = ocir.saved_things,
      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
      ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
      ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
    ) %>%
    add_numeric(., exclude = exclude_cols) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad ocir head}
if(GLAD == TRUE | EDGI == TRUE) {
head(prepan.ocir.raw.id)
}
```

```{r glad ocir summary}
if(GLAD == TRUE | EDGI == TRUE) {
summarytools::dfSummary(
  prepan.ocir.raw.id,
  graph.col = F,
  valid.col = F
  )
}
```

>>>>

@@

# Prepandemic

## gad (prepan)

```{r glad prepan gad head}
if(GLAD ==TRUE | EDGI == TRUE){
head(prepan.gad.raw.id)
}
```

```{r glad prepan gad summary}
if(GLAD ==TRUE | EDGI == TRUE){
summarytools::dfSummary(
  prepan.gad.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```

## pcl (prepan)

@@

@@

```{r pcl prepan head}
if(GLAD == TRUE | EDGI == TRUE){
head(prepan.pcl.raw.id)
}
```

```{r pcl prepan summary}
if(GLAD == TRUE | EDGI == TRUE){
summarytools::dfSummary(
  prepan.pcl.raw.id,
  graph.col = F,
  valid.col = F, labels.col = F)
}
```

## phq (prepan)

@@

@@

```{r phq prepan head}
if(GLAD == TRUE | EDGI == TRUE) {
head(prepan.phq.raw.id)
}
```

```{r phq prepan summary}
if(GLAD == TRUE | EDGI == TRUE) {
summarytools::dfSummary(
  prepan.phq.raw.id,
  graph.col = F,
  valid.col = F
  )
}
```

## ocir (prepan)

```{r glad ocir prepan cols}
if(GLAD == TRUE){
glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_glad.rds"))
dim(glad.ocir.raw)
colnames(glad.ocir.raw)
}
```

```{r glad ocir prepan cleaning}
if(GLAD == TRUE){
glad.ocir.raw.id <- glad.ocir.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
    ocir.arranged_things_prepan = ocir.arranged_things,
    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
    ocir.saved_things_prepan = ocir.saved_things,
    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r edgi ocir prepan cols}
if(EDGI == TRUE){
  edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_edgi.rds"))
  dim(edgi.ocir.raw)
  colnames(edgi.ocir.raw)
}
```

```{r edgi ocir prepan cleaning}
if(EDGI == TRUE){
  edgi.ocir.raw.id <- edgi.ocir.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID),
           startDate.prepandemic = startDate) %>% # Rename startDate
    select(
      Sample, # Sample
      ID, # ID
      ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
      ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
      ocir.arranged_things_prepan = ocir.arranged_things,
      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
      ocir.saved_things_prepan = ocir.saved_things,
      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
      ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
      ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
    ) %>%
    add_numeric(., exclude = exclude_cols) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r ocir prepan head}
if(GLAD == TRUE | EDGI == TRUE) {
head(prepan.ocir.raw.id)
}
```

```{r ocir prepan summary}
if(GLAD == TRUE | EDGI == TRUE) {
summarytools::dfSummary(
  prepan.ocir.raw.id,
  graph.col = F,
  valid.col = F
  )
}
```
